Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-17 vesicle_code/docs/adhesion/adhesion.tex
more changes from yn

 Large value of $m$ corresponds to a sharp increase in repulsion force as two objects are within the separation distance $\delta$.
 This poses great challenges for simulations as the numerical time-marching can be very stiff (i.e., very small time step) for large $m$. 
 The adaptive time-stepping BIE scheme makes it possible to simulate vesicle adhesive dynamics with specified numerical precision for reasonable computation time.
 We explore several combinations of $(m,n)$ in the simulations 
 of two vesicles forming a doublet in a quiescent flow, 
 and found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
\todo[inline]{Concluding remarks}

@@

>>>>

 Large value of $m$ corresponds to a sharp increase in the repulsion force as two objects are within the separation distance $\delta$.
 This poses great challenges for simulations as the numerical time-marching can be very stiff (i.e., very small time step) for large $m$. 
 The adaptive time-stepping BIE scheme makes it possible to simulate vesicle adhesive dynamics with specified numerical precision for reasonable computation time.
 We explore several combinations of $(m,n)$ in the simulations 
 of two vesicles forming a doublet in a quiescent flow.
 We found very little difference in both the dynamic evolution and equilibrium configuration between $(m,n)=(8,6)$ and $(m,n)=(4,2)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
\todo[inline]{Concluding remarks}
In this work we use boundary integral formulation with adaptive time-stepping  to simulate hydrodynamics of two vesicles with adhesive interactions.
In a quiescent flow,  two vesicles move towards each other under a long-range attraction when they are in close vicinity of each other.
We use a lubrication theory to estimate the time it takes to reach the separation distance, and found the theoretical scaling to be in good agreement with numerical results.  
Once two membranes are within separation distance $\delta$, the adhesive force turns repulsive and the membranes flatten to form a contact region.
Our simulations show that the membranes in the contact region are actually curved with end points at the shortest distance. 
Once a vesicle doublet forms, we examine the dependence of membrane bending and adhesion energies on reduced area, Hamakar constant and separation distance.

Next we conduct a numerical experiment where a vesicle doublet is placed at the center of a fluid trap, which in microfluidic laboratory 
can be actively controlled so that fluid trap center is effectively a stagnation point in an extensional flow characterized by a extensional flow rate.
At low flow rate, we find the doublet to rotate ninety degrees to align with the flow such that 
the long axis of the doublet is along the divergent axis and the convergent stream is pushing the two vesicles
together. As the flow rate increases the vesicle doublet rotates less and we observe tank-treading like motion of both vesicles in the doublet.
When the flow rate reaches above the critical value, the diverging flow pulls the vesicles apart before the doublet has time to rotate to remain intact.
These results indicate that it is possible to use the fluid trap to separate a vesicle doublet under adhesion, and thus provide a means to
probe the adhesion strength between membranes. {\color{red} For adhesion energy blahblahblah, an extensional flow rate sososo is required to separate the doublet from our
simulations. IS THIS PLAUSIBLE?}
We hope that our simulations might inspire microfluidic experiments.

We also examine how adhesive interaction may lead to formation of a vesicle doublet dynamically in flowing conditions.
We simulate two vesicles approaching each other in a planar shear flow, and examine how their adhesive interactions lead to doublet formation.
Once a doublet forms, the two vesicle membranes rotate around each other as they deform dynamically. The usual tank-treading motion of a vesicle under shear flow is not 
observed in each of the two vesicles. We also compute the effective shear viscosity of a dilute suspension of vesicle doublets, and found that membrane adhesion contribution
increases with decreasing reduced area because deflated vesicles (low reduced area) deform more easily and more membranes in the contact region.

In our formulation we did not include any electrostatic interactions between membranes under adhesion. When the electrostatic interaction is important, an electro-osmotic pressure
in the thin film is found to be responsible for the observed membrane undulation \cite{LiraDimova}.

@@

\acknowledgments

YNY would like to acknowledge helpful discussions with 
The authors acknowledge support from NSF-DMS 1614863 and 1412789 (YNY).
